A better way to format your document for CEUR-WS

### 2024-06-23 paper/sections/00-title-abstract.tex
Add introduction first draft
Minor typo in readme

%%
%% This command is for the conference information            %%%%%%% TODO !!! UPDATE THIS %%%%%%
\conference{Woodstock'22: Symposium on the irreproducible science,
  June 07--11, 2022, Woodstock, NY}

@@

% Authors
\author[1]{Darren Rawlings}[%
email=abc@def.ghi,
url=https://startung.github.io/,
]
\address[1]{University of Groningen, Broerstraat 5, 9712 CP Groningen, Netherlands}

\author[]{Tim Chopard}[%
email=timchopard@pm.me,
url=http://cloudberries.io,
]

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  LaTeX class \sep
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

>>>>

%%
%% This command is for the conference information            %%%%%%% TODO !!! UPDATE THIS %%%%%%
\conference{CLEF 2024: Conference and Labs of the Evaluation Forum, September 9-12, 2024, Grenoble, France}

@@

% Authors
\author[1]{Darren Rawlings}[%
email=abc@def.ghi,
url=https://startung.github.io/,
]
\fnmark[1]
\address[1]{University of Groningen, Broerstraat 5, 9712 CP Groningen, Netherlands}

\author[]{Tim Chopard}[%
email=timchopard@pm.me,
url=http://cloudberries.io,
]
\fnmark[1]

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Multi-Label classification\sep
  Principal component analysis\sep
  ResNet\sep
  Vision Transformers\sep
  XGBoost\sep
  GeoLifeCLEF 2024\sep
  CEUR-WS
\end{keywords}

### 2024-06-23 paper/sections/04-method.tex
Minor typo in readme

In order to manage the multilabel classification required for this research we implemented an ensemble approach.
This section details the individual architectures and the methods used to combine them.

@@

\subsubsection{Principal Component Analysis}
Principal Component Analysis (PCA) is a method for reducing dimensionality~\cite{pcapaper}. It functions by projecting the high dimensional data onto the direction of maximum variance, thus retaining key features and reducing noise.

@@

\subsubsection{Preprocessing}

>>>>

In order to manage the multilabel classification required for this research we implemented three main approaches as well as ensemble combinations of each approach.
This section details the data preprocessing as well as the individual architectures and the methods used to combine them.

\subsection{Preprocessing}

The Prsence-Absence Metadata, Environmental rasters and Time-Series Satellite data were preprocessed.

\subsubsection{Dimensionality Reduction with Principal Component Analysis}
Principal Component Analysis (PCA) is a method for reducing dimensionality~\cite{pcapaper}. 
It functions by projecting the high dimensional data onto the direction of maximum variance, thus retaining key features and reducing noise.

We applied PCA to much of the Time Series data within the Environmental Rasters. Each month in a given class

\subsubsection{Missing and infinite values}

\subsubsection{Low-Value Data Removal}

% The raw data included some missing, or infinite values that needed to be processed prior to model fitting. When a column was both deemed important to model fitting and contained such values, these values were replaced by the mean so as to avoid excessive influence from outliers without overly effecting the shape of the data~\cite{missingmedian}.
% 
% \textbf{TODO: Further explanation when models finalized}

% The Metadata and Bioclimatic Rasters were preprocessed for use in the count and XGBoost models in order to both reduce dimensionality and remove potential noise.

@@

@@

In addition, the number of viable output species was reduced from 11255 (the total species present accross all data) down to 1141 (the total species with more than 100 occurrences in the presence/absence data). 
This reduction served to remove several edge cases and focus the models more on likelier species.
